\documentclass[acmsmall, screen, review, anonymous]{acmart}
\settopmatter{printfolios=true,printccs=false,printacmref=false}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
%\usepackage[dvipsnames]{xcolor}
%\usepackage{cite}
\usepackage[most]{tcolorbox}
%\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{textcomp}
\usepackage{mathtools}
\usepackage[shortlabels]{enumitem}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{tabularx}
\usepackage{bbm}
%\usepackage{unicode-math}
\usepackage[utf8]{inputenc}
\usepackage{newunicodechar}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{adjustbox}

%% PL packages
\usepackage{stmaryrd} 
\usepackage{proof}
\usepackage{mathpartir}
%\usepackage{color}
\usepackage{xstring}
\usepackage{xspace}
\usepackage{turnstile}

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{none}


%%
%% These commands are for a JOURNAL article.
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{ICFP} 
\acmArticle{1}
\acmYear{2022}
\acmMonth{9}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

\citestyle{acmauthoryear}


\begin{document}
\usetikzlibrary{matrix, arrows.meta, calc, positioning}
\tikzset{myarrow/.style={-Latex, rounded corners},}

\newcommand*\emptycirc[1][1ex]{\tikz\draw (0,0) circle (#1);} 
\newcommand*\halfcircleft[1][1ex]{%
  \begin{tikzpicture}
  \draw[fill] (0,0)-- (90:#1) arc (90:270:#1) -- cycle ;
  \draw (0,0) circle (#1);
  \end{tikzpicture}}
\newcommand*\halfcircright[1][1ex]{%
  \begin{tikzpicture}
  \draw[fill] (0,0)-- (0:#1) arc (0:90:#1) -- cycle ;
  \draw[fill] (0,0)-- (270:#1) arc (270:360:#1) -- cycle;
  \draw (0,0) circle (#1);
  \end{tikzpicture}}
\newcommand*\fullcirc[1][1ex]{\tikz\fill (0,0) circle (#1);} 

\newcolumntype{R}[2]{
	>{\adjustbox{angle=#1, lap=\width-(#2)}\bgroup}
	c
	<{\egroup}
}
\newcommand*\rot{\multicolumn{1}{R{30}{1.5em}}}


\definecolor{vert}{RGB}{0,181,0}
\definecolor{oran}{RGB}{223,74,0}
\definecolor{viol}{RGB}{134,0,175}
\definecolor{roug}{RGB}{215,15,0}
\definecolor{bb}{RGB}{0,0,0}
\definecolor{gg}{RGB}{220,220,220}
\definecolor{royalblue}{rgb}{0.25, 0.41, 0.88}
\definecolor{forestgreen}{rgb}{0.13, 0.55, 0.13}
\definecolor{YellowOrange}{rgb}{0.98, 0.6, 0.01}
\definecolor{Red}{rgb}{0.89, 0.0, 0.13}
\definecolor{Black}{rgb}{0.0, 0.0, 0.0}
\definecolor{Purple}{rgb}{0.63, 0.36, 0.94}
\definecolor{purp}{rgb}{0.59, 0.48, 0.71}

\newcommand{\anote}[1]{{\color{magenta}{AM: {{#1}}}}}
\newcommand{\snote}[1]{{\color{green}{SB: {{#1}}}}}

\newtcolorbox[auto counter]{bbox}[2][]{%
    colback=white,
    colframe=bb,
    %colbacktitle=white!90!roug,
	colbacktitle=white!40!gg,
    coltitle=black,
    fonttitle=\small\bfseries, 
	fontupper=\small,
	fontlower=\small,
    enhanced,
    attach boxed title to top left={yshift=-2mm, xshift=0.5cm},%
    #1,% For possible options
}

\mathchardef\hyp="2D
\mathchardef\car="5E

\makeatletter
\newcommand\BeraMonottFamily{%
	\def\fvm@scale{0.85}%
	\fontfamily{fvm}\selectfont
}
\makeatother

\title{Eventually
}

\input{macros}
\input{st-macros}

\begin{abstract}
Software tooling for UC programming. Strongl typed language like Haskell we can define contexts for UC protocols/proofs in a modular way.
Results in on-paper definitions that can use clean abstractions through shell processes, and makes code easy.
We present Eventually and Optionally constructions and realize an ABA protocol using it. 
Show fuzz testing as tool for protocol analysis to discover buggy / in-secure code.
Fuzzing on ACast to detect problems with the code (relates directly to the ABA fuzzing because it is also an issue of thresholds).
Future work / discussion: contexts for more complex things like MPC. Write code directly but it translates to MPC instructions with the appropriate
communication assumptions.

\end{abstract}

\maketitle


%\begin{IEEEkeywords}
%component, formatting, style, styling, insert
%\end{IEEEkeywords}

\section{Introduction}
\input{sections/intro}

\section{Background} \label{sec:background}
\input{sections/background}

\section{Related Works} \label{sec:related}
\input{sections/relatedworks}

\section{Discussion and Future Work}
\input{sections/discussion}

\bibliographystyle{ACM-Reference-Format}
\bibliography{nomosuc}

\newpage

\appendix

\pagebreak

\end{document}
