\begin{theorem}\label{thm:bracha:sync}
Let $\Pi_{\msf{bracha}}$ and $\mathcal{F}_{\msf{bracha}}$ be $\overline{\mathcal{W}}_{\msf{sync}}$-subroutine respecting protocols. 
Then $\Pi_{\msf{bracha}}$ EUC-realizes $\mathcal{F}_{\msf{bracha}}$ in the $\mathcal{F}^{n(n-1)}_{\msf{sync}}$-hybrid world in the static corruptions ($t < \frac{n}{3}$) model for any $\overline{\mathcal{W}}_{\msf{sync}}$-externally constrained, weakly-balanced environment $\mathcal{Z}$. We have:

$$\textsc{EXEC}^{\Wsync}_{\mathcal{F}_{\msf{bracha}}, \Ssyncbracha, \Environment} \approx \textsc{EXEC}^{\Wsync}_{\pi_{\msf{bracha}}, \Dadv, \Environment}$$
\end{theorem}

\textit{Proof of Theorem \ref{thm:bracha:sync}.}

We first construct the simulator \Ssyncbracha. 
The full pseudo-code of \Ssyncbracha~ is shown in Figure~\ref{fig:sim:bracha:sync} however, for brevity, we describe it here.

\Ssyncbracha~ runs a full simulation of the real world internally with its own copy of the the wrapper, \Wsync'. It also maintains a copy the \msf{runqueue} in \Wsync and its \msf{delay}. 
It also requests leaks from \Wsync every time is it is activted with input from the wrapper (\Advance), or the enviromnent (corrupt input, \Delay, \Exec).

\heading{Simulating Honest Input to \Fbracha.}
The honest input to \Fbracha is leaked to \Ssyncbracha~ when requesting leaks from \Wsync. 
It passes the input to it's internally simulated dealer $\mathcal{D}'$ and increments its internal \msf{delay}.

\heading{Simulating Other Codeblocks.}
For all other scheduled code blocks (from other protocol sessions), it adds those corresponding codeblocks to \Wsync' and updates its copy of \msf{runqueue} and \msf{delay}.

\heading{Simulating Corrupt Input.} When the simulator receives corrupt input for some party $\pi_i$ it simply passes the input to its internal copy of it, $\pi_i'$. In the case of Bracha, only the dealer submit input to the ideal functionality, though \Ssyncbracha~ waits to give input to the corrupted dealer until the simulation commits to an input.

\heading{Simulating a \msf{Poll} Call by the Environment.}
For every \msf{Poll} to \Wsync that does not execute a codeblock (it's delay is positive), \Ssyncbracha~ is activated with the \msf{poll} message.
The simulator updates its internal $\msf{delay}$ and adds 1 unit of delay to \Wsync if it is 0 (does not want the environment to control when the next codeblock is executed).
Then it simulates \msf{poll} to \Wsync' and stores any new leaks from it.

\heading{Handling Codeblocks in the Simulation.}
When a codeblock executes in the simulation \Ssyncbracha~ executes the corresponding codeblock in the ideal world if it was schedules by a protocol session other than the challenge protocol.
When a simulated honest challenge protocol party, $\pi_i'$, outputs a value $v$, i.e. commits to a value, \Ssyncbracha:
\begin{itemize}
\item If the dealer is corrupt, \Ssyncbracha~ gives input $v$ to the corrupt ideal world dealer if this is the first such output. It then executes the outer codeblock from \Fbracha. It then executes the codeblock that outputs $v$ to $\pi_i$ in the ideal world.
\item If the dealer is honest, the codeblocks already exist and it executes the one which delivers output to $\pi_i$.
\end{itemize}

\heading{Simulating \Exec Calls.}
When activated by \Environment with an \Exec call, it forwards the call to it's internal simulated adversary. If a codeblock is executed, it responds as specified above. 

\heading{Handling Corrupt Simulated Output.} 
\Ssyncbracha outputs all corrupt party output from the simulated adversary to the environment.
