\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage[dvipsnames]{xcolor}
\usepackage{cite}
\usepackage[most]{tcolorbox}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{textcomp}
\usepackage{mathtools}
\usepackage[shortlabels]{enumitem}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{tabularx}
\usepackage{bbm}

%% PL packages
\usepackage{stmaryrd} 
\usepackage{proof}
\usepackage{mathpartir}
\usepackage{color}
\usepackage{xstring}
\usepackage{xspace}
\usepackage{turnstile}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\usetikzlibrary{matrix, arrows.meta, calc, positioning}
\tikzset{myarrow/.style={-Latex, rounded corners},}

\definecolor{vert}{RGB}{0,181,0}
\definecolor{oran}{RGB}{223,74,0}
\definecolor{viol}{RGB}{134,0,175}
\definecolor{roug}{RGB}{215,15,0}
\definecolor{bb}{RGB}{0,0,0}
\definecolor{gg}{RGB}{220,220,220}

\newcommand{\anote}[1]{\textcolor{magenta}{AM: #1}}

\newtcolorbox[auto counter]{bbox}[2][]{%
    colback=white,
    colframe=bb,
    %colbacktitle=white!90!roug,
	colbacktitle=white!40!gg,
    coltitle=black,
    fonttitle=\bfseries, 
    enhanced,
    attach boxed title to top left={yshift=-2mm, xshift=0.5cm},%
    #1,% For possible options
}

\mathchardef\hyp="2D
\mathchardef\car="5E

\makeatletter
\newcommand\BeraMonottFamily{%
	\def\fvm@scale{0.85}%
	\fontfamily{fvm}\selectfont
}
\makeatother

\title{Nomos-UC: a programming framework for cryptography based on resource-aware session types\\
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\input{macros}
\input{st-macros}

\author{\IEEEauthorblockN{Given Name Surname}
\IEEEauthorblockA{\textit{University of Science}}
\and
\IEEEauthorblockN{Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)}}
\and
\IEEEauthorblockN{Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)}}
\and
\IEEEauthorblockN{Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)}}
\and
\IEEEauthorblockN{Fiven Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)}}
\and
\IEEEauthorblockN{Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)}}
}

\maketitle

\begin{abstract}
The Universal Composability (UC) framework is the leading framework for analyzing cryptographic protocols and their applications.
Many tools exist, currently, for analyzing protocol in the UC framework, however, many of them fall short of adequatley capturing its full polynomial time notion and aid in expressing complex, modular protocols.
In this work we adapt work into resource-aware session types~\cite{dasnomos} to the UC setting and use their existing potential mechanism to implement the new import mechanism introduced by~\cite{uc}.
Resource-aware session types enforce protocol specifications and runtime budgets in the type system, aiding in the construction of large, modular protocols.

To the best of our knowledge this is the first work to meaningfully implement and use the novel import mechanism, and we demonstrate its usefulness through a case study of the two-party commitment protocol~\ref{rocommitment}.
\todo{add more}
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
\input{sections/intro}

\section{Background} \label{sec:background}
\input{sections/background}

\section{Nomos UC} \label{sec:nomosuc}
\input{sections/nomosuc}

\section{Related Works}
\input{sections/relatedworks}

%\section{Import}
%\input{sections/import}

\section{ExecUC} \label{sec:execuc}
\input{sections/execuc}

\section{Commitment} \label{sec:commitment}
\input{sections/commitment}

%\section{Multisession Operator}
%\input{sections/multisession}

%\section{Programming-Friendly Communication Models for UC} \label{sec:wrappers}
%\input{sections/wrappers}
%
%\section{Reliable Broadcast} \label{sec:rbc}
%\input{sections/rbc}

\section{Discussion and Future Work}
\input{sections/future}

\section*{References}


\bibliographystyle{ACM-Reference-Format}
\bibliography{nomosuc}

%input{figures/asyncwrapper}

\appendix

\section{\fwrapper} \label{app:fwrapper}
The \fwrapper adopts a similar approach to the \partywrapper, except it only creates one instance of the underlying functionality.
For the same reason as the \partywrapper, we use an \fwrapper to enable a dynamic set of parties.
One caveat in supporting such functionalities, is that, so far, only functionalities whose type follows a specific form are allowed.
In the random oracle type given below, notice that the type before and after a party interacts with it is the same: type $\m{party}[a]$.
\begin{mathpar}
\m{party}[a] = \textcolor{red}{\getpot^1} \ichoice{\mb{hash} : \m{pid} \arrow \m{int} \product \m{hashing}[a]} \\
\m{hashing}[a] = \echoice{\mb{shash} : \m{pid} \arrow \m{int} \product \textcolor{red}{\paypot^0} \m{party}[a]} 
\end{mathpar}
A party queries a $\mb{hash}$ of an integer from \Fro and receives an integer as a response. The session type includes the \inline{pid}, which enables it to handle all parties over the same channel.

An example of the internals of the \fwrapper are showing on the left-hand-side of Figure~\ref{fig:multisession}.
Like the \inline{z2p} processes in the \partywrapper, \inline{S} and \inline{R} represent the sender and receiver in the commitment protocol, and they read from their virtual communicators and communicate with \Fcom over a session-typed channel.


%\section{Proofs}
%\input{sections/brachaproof}

%\input{sections/enoughimport}

\pagebreak

%\begin{figure}
%\input{figures/fasync}
%\end{figure}

%\begin{figure}
%\input{figures/frbc}
%\end{figure}

%\begin{figure}
%\input{figures/protbracha}
%\end{figure}
%
%\begin{figure}
%\input{figures/simbrachaasync}
%\end{figure}
%
%\begin{figure}
%\begin{subfigure}{\columnwidth}
%\input{figures/algopoll}
%\end{subfigure}
%%\begin{subfigure}{\columnwidth}
%%\input{figures/algosimgetleaks}
%%\end{subfigure}
%\begin{subfigure}{\columnwidth}
%\input{figures/algosimpartyout}
%\end{subfigure}
%\end{figure}
%
%
%\input{figures/F_state}



\end{document}
