%\documentclass[acmsmall, screen, review, anonymous]{acmart}
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
%\settopmatter{printfolios=true,printccs=false,printacmref=false}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
%\usepackage[dvipsnames]{xcolor}
%\usepackage{cite}
\usepackage[most]{tcolorbox}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{textcomp}
\usepackage{mathtools}
\usepackage[shortlabels]{enumitem}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{tabularx}
\usepackage{bbm}
%\usepackage{unicode-math}
\usepackage[utf8]{inputenc}
\usepackage{newunicodechar}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{adjustbox}
\usepackage{float}
\usepackage{hyperref}

%\usepackage{soul}
%\usepackage{color}
%\let\st\undefined

%% PL packages
\usepackage{stmaryrd} 
\usepackage{proof}
\usepackage{mathpartir}
%\usepackage{color}
\usepackage{xstring}
\usepackage{xspace}
\usepackage{turnstile}



\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
%\setcopyright{none}


%%
%% These commands are for a JOURNAL article.
%\acmJournal{PACMPL}
%\acmVolume{1}
%\acmNumber{ICFP} 
%\acmArticle{1}
%\acmYear{2022}
%\acmMonth{9}
%\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
%\startPage{1}

%\citestyle{acmauthoryear}


\begin{document}
\usetikzlibrary{matrix, arrows.meta, calc, positioning}
\tikzset{myarrow/.style={-Latex, rounded corners},}

\newcommand*\emptycirc[1][1ex]{\tikz\draw (0,0) circle (#1);} 
\newcommand*\halfcircleft[1][1ex]{%
  \begin{tikzpicture}
  \draw[fill] (0,0)-- (90:#1) arc (90:270:#1) -- cycle ;
  \draw (0,0) circle (#1);
  \end{tikzpicture}}
\newcommand*\halfcircright[1][1ex]{%
  \begin{tikzpicture}
  \draw[fill] (0,0)-- (0:#1) arc (0:90:#1) -- cycle ;
  \draw[fill] (0,0)-- (270:#1) arc (270:360:#1) -- cycle;
  \draw (0,0) circle (#1);
  \end{tikzpicture}}
\newcommand*\fullcirc[1][1ex]{\tikz\fill (0,0) circle (#1);} 

\newcolumntype{R}[2]{
	>{\adjustbox{angle=#1, lap=\width-(#2)}\bgroup}
	c
	<{\egroup}
}
\newcommand*\rot{\multicolumn{1}{R{30}{1.5em}}}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}

\definecolor{vert}{RGB}{0,181,0}
\definecolor{oran}{RGB}{223,74,0}
\definecolor{viol}{RGB}{134,0,175}
\definecolor{roug}{RGB}{215,15,0}
\definecolor{bb}{RGB}{0,0,0}
\definecolor{gg}{RGB}{220,220,220}
\definecolor{royalblue}{rgb}{0.25, 0.41, 0.88}
\definecolor{forestgreen}{rgb}{0.13, 0.55, 0.13}
\definecolor{YellowOrange}{rgb}{0.98, 0.6, 0.01}
\definecolor{Red}{rgb}{0.89, 0.0, 0.13}
\definecolor{Black}{rgb}{0.0, 0.0, 0.0}
\definecolor{Purple}{rgb}{0.63, 0.36, 0.94}
\definecolor{purp}{rgb}{0.59, 0.48, 0.71}

\newcommand{\anote}[1]{{\color{magenta}{AM: {{#1}}}}}
\newcommand{\snote}[1]{{\color{green}{SB: {{#1}}}}}

\newtcolorbox[auto counter]{bbox}[2][]{%
    colback=white,
    colframe=bb,
    %colbacktitle=white!90!roug,
	colbacktitle=white!40!gg,
    coltitle=black,
    fonttitle=\footnotesize\bfseries, 
	fontupper=\footnotesize,
	fontlower=\footnotesize,
    enhanced,
    attach boxed title to top left={yshift=-2mm, xshift=0.5cm},%
    #1,% For possible options
}

\mathchardef\hyp="2D
\mathchardef\car="5E

\makeatletter
\newcommand\BeraMonottFamily{%
	\def\fvm@scale{0.85}%
	\fontfamily{fvm}\selectfont
}
\makeatother

\title{NomosUC: a programming framework for cryptography based on resource-aware session types\\
%\thanks{Identify applicable funding agency here. If none, delete this.}
}

\input{macros}
\input{st-macros}

\maketitle

\begin{abstract}
  Universal Composability (UC) is a leading definitional framework for secure protocols used in cryptography
  and broadly in computer security.
  However, compared with traditional game-based definitions, UC has been less studied from the viewpoint
  of programming language semantics and formal methods.
  This work introduces a novel programming abstraction called \emph{import
  session types} (IST) to express UC functionalities and protocols.
  This new abstraction is inspired by \emph{resource-aware session types} (Rast), a recently designed type system
  for analyzing execution cost of concurrent message-passing systems.
  Session types are a typed framework for describing bi-directional communication protocols in a distributed system
  that are statically enforced via type-checking.
  Rast enhances this framework by adding \emph{potential annotations} to these communication protocols
  that modularly describe their abstract execution cost.
  IST establishes a close correspondence between Rast and UC where session types can be used
  to describe the communication patterns of the Interactive Turing Machines in a UC protocol.
  Moreover, IST can be used to encode and statically enforce the \emph{import mechanism} in UC used to
  ensure polynomial-time computation.
  We therefore combine Nomos, an existing language based on Rast, with ILC, a process-based core calculus for UC,
  to build a new language called NomosUC.
  Designing NomosUC required solving a range of technical challenges.
  While session types are naturally linear and prevent cyclic topologies, UC 
  allows adversaries the freedom to adaptively steer the communication.
  Also, since UC makes use of sandbox execution and other generic composition operations,
  reconciling UC \emph{import} with Rast \emph{potential} required introducing a hierarchy of virtual tokens.
  To validate our design, we work through the standard theory of UC composition operators, and complete
  a UC proof of security for the cryptographic commitment. 
\end{abstract}



%\begin{IEEEkeywords}
%component, formatting, style, styling, insert
%\end{IEEEkeywords}

\section{Introduction} \label{sec:intro}
\input{sections/intro}

\section{Background on Universal Composability} \label{sec:background}
\input{sections/background}

\section{A Commitment Protocol in NomosUC} \label{sec:example}
\input{sections/example}

\section{Base System of Session Types in NomosUC} \label{sec:basic}
\input{sections/baselang}

\section{Import and Potential in NomosUC} \label{sec:import}
\input{sections/importlang}

\section{Type Safety of NomosUC} \label{sec:safety}
\input{sections/safety}

\section{The UC Experiment} \label{sec:execuc}
\input{sections/execuc}

\section{Sandboxing} \label{sec:commitment}
\input{sections/commitment} 

%\section{Ideal Functionalities} \label{sec:idealfs}
%\input{sections/functionalities}
%\section{Coin Flipping and Commitment} \label{sec:commitment}
%\input{sections/commitment}


\section{Related Works} \label{sec:related}
\input{sections/relatedworks}

\section{Future Work}
\input{sections/future}

\bibliographystyle{IEEEtran}
\bibliography{nomosuc}

\newpage

%input{figures/asyncwrapper}

%\appendix
\appendices

\section{Emulation Continued} \label{app:emulation}
\input{appendix/emulationcont}

\section{Selected Typing Rules for NomosUC} \label{app:typing_rules}
\input{appendix/typing_rules}

\section{Arbitrary Parties} \label{app:arbparties}
\input{appendix/arbparties}

\section{Dummy Lemma} \label{app:dummy}
\input{appendix/dummylemma}

\section{Multisession Theorems} \label{app:ms}
\input{appendix/bangf}

\section{Commitment Protocol} \label{app:protcom}
\input{appendix/protcom}

\section{Coin Flipping} \label{app:flip}
\input{appendix/coinflip}

\section{ITM Completeness} \label{app:itm}
\input{appendix/itmiffnomosuc}

\pagebreak

\end{document}
