% RESEARCH QUESTIONS:
%     (RQ1). Is UC suitable and practical as a development framework rather than only a theoretical framework?
%             (i). Can existing UC models/techniques be improved for an engineering purpose?
%             (ii). What are the advantages of using UC for development?
%     (RQ2). Is UC as a development framework compatible with existing informal analysis techniques?
%             (i).  Fuzz testing is widely used, is a successful analysis tool, and is itself an engineering undertaking. Can we successful apply fuzzing to UC?
%             (ii).  Does the ideal functionality model and out realization of import aid in analyzng liveness in distributed protocols?

% UC is leading framework but only recently we see it being used for distributed systems
% UC is good at expressing certain kind of properties easily through an ideal functionality 
Universal composability is the leading framework for defining the security of
message-passing cryptographic protocols between mutually distrustful parties.
Though largely used for cryptography, it has experienced a surge of interest in
the domain of asynchronous distributed systems literature within the last 10
years.  This is due, in large part, to the rising interest in modelling
decentralized byzantine protocols, namely blockchain
protocols~\cite{kosba2016hawk, badertscher2018ouroboros, miller2019sprites,
badertscher2024bitcoin, dziembowski2018fairswap, aumayr2021blitz,
kiayias2020composable}.
%The framework's appeal is two-fold. 
The framework has widespread appeal for a few reasons.  First, the ideal
functionality model for specifying protocol behavior allows the designer to
express properties not easily captured via a property-based definitions,
clearly define adversarial capabilities, and reason about what the adversary
learns, and it reduces security definitions down to an indistinguishability
relationship to an ideal execution.  Second, the modularity encouraged by the
framework, and the subsequent composition operators and theorems, are
well-suited to distributed systems where protocols sit on a bed of several
other layered distributed protocols, and creating composable security proofs in
isolation is a big advantage.  Finally, the computational model of UC allows
proving liveness of a protocol within an eventual delivery system against a
computationally bounded adversary--a core innovation of the framework.

% Async systems well-suited to the UC domain
% little work has attempted using informal setting and why? 
Protocols like distributed randomness generation (two-party coin flips,
$n$-party common coin protocols) exhibit properties such as fairness, that may
bounds on adversarial influence on protocol output, and require a specific
output distribution.  These requirements make asynchornous systems particularly
well-suited to UC.  Most modern byzantine protocols rely such protocols as
subroutines, or themselves exhibit similar properties, and the UC framework
provides a generalized approach to specifying and defining their security in
relation to a computationally bounded adversary and environment.  Despite these
advantages of the framework, little work has explored the use of UC as an
analysis \emph{and implementation} framework for distributed protocols, and to
the best of our knowledge no generalizable framework currently exists which
exhibits all of these features.  Implementations of UC definitions are often
done in frameworks that bare little resemblance to it, and the resulting code
has a weak connection to the proofs in literature.  The primary reason for the
disparity is that UC is a subtle and complex framework that is considered
accessible only to seasoned researchers or experts on the topic.  Furthermore
the question remains whether the framework remains useful or even advantageous
in an informal setting where proofs are replaced by software testing.  UC
definitions, themselves, also pose a challenge because existing proofs, ideal
functionalities, and protocols can be large, difficult to understand, and often
contain framework-specific details alongside core
functionality~\cite{badertscher2024bitcoin, badertscher2018ouroboros}
%In this work we implement UC in a mainstream language, introduce a new model for asynchronous networks, propose new UC design principles to simplify and isolate user code from framework-specific code, and examine the framework through a few case studies.

% existing UC programming tools and their push towards more formality 
Existing literature focuses on creating programming languages for UC or formal
programming tools that express UC in existing
languages~\cite{canetti2019easyuc, liao2019ilc}.  Despite enabling executable
UC definitions, most work aims to enable formal analysis or proof generation
targetted towards researchers and do very little to bridge the game between
theory and implementation.

%However, these works exacerbate the biggest challenge to UC adoption oustide of academics: is requires a lot of esoteric knowledge and expertise to parse the subtle details of UC proofs, constructions, and mechanisms.
%Translating UC definitions of protocols from literature to an implementation presents its own challenges.
%Definitions are highly technical and full of framework-specific or model-specific details, and implementing them in a non-UC programming framework requires significant tranlation work.
%Existing UC definitions for distributed protocols, existing largely in the blockchain space~\cite{bitcoinledger, ouroboros, perun}, consist of ideal functionalities, sub-protocols, and proofs that are many pages long. 
%Understanding and attempting to falsify such weildy definitions can be difficult, let alone implementing them correctly. 

% highlights of drawbacks of existing development/analysis frameworks in distributed systems
% TODO: talk about the analysis drawbacks as well
%Existing frameworks and tooling for implementing and analyzing distributed protocols fall short of performing such analysis.
%Several works, for example, rely on TLA-style specifications which are able to specify safety and liveness properties but not properties about probability distributions~\cite{a, bunch, of, them}.
%Furthermore, many of them tolerate only crash faults and are unable to express any properties related to byzantine adversaries.
%For example, even simple two-party com
%putations (2PC) require reasoning about how the adversary chooses its input, what it learns, and whether inputs of other parties is kept secret.

% the central claim and research questions of this work
In this work we instantiate UC as a development framework for asynchronous
distributed protocols and explore its use for implementing and analyzing them.
Notably, we take the opposite approach of existing works and only consider
informal analysis of protocols within the framework.  Concretely our research
questions are stated below, and we expand on, and discuss, them in the
remainder of this section.
\begin{enumerate}
\item How are asynchronous eventual delivery protocols realized in UC, and what
are the design consequences?
\item What are the advantages or drawbacks of developing protocols in UC
compared to existing frameworks?
\item To what extent can the advantages of the real-ideal paradigm and ideal
functionality model be captured by informal analysis of UC implementations?
\end{enumerate}
Our focus on \emph{informal analysis} extends from our stated goal of
minimizing the barriers to accessibility.  We select fuzz testing as our
informal analysis tool of choice, because test case generation and analysis
fits well within UC's emulation definition (more detail in
Section~\ref{sec:background}) for ensuring indistinguishability of a protocol
with an ideal program for all environments (the test cases of UC) and
adversaries.

% talking about the first research question
Our first challenge in implementing a UC framework for asynchronous development
is contending with the new \emph{import mechanism} for polynomial time in UC
and understanding the consequences of its design for eventual delivery and
liveness.  Existing asynchronous models in UC work with the outdated
lenght-of-input polynomial time notion, which has been shown to permit infinite
executions through a straightforward protocol.  Existing definitions also
impose additional design constraints on ideal functionalities, protocols, and
environments that unnecessarily force framework and model-specific code to
exist within application code.  The import mechanism centers around import, the
fundamental unit of potential runtime that is exchanges as ``tokens'' between
machines, giving them the potential to perform polynomial work based on the net
import held.  To the best of our knowledge, no work has explored how eventual
delivery is defined with import, what the consequences of it are for protocol
design, and how liveness properties are expressed.  Concretely, we propose a
new eventual delivery model that uses import, and we outline a set of design
decisions that minimize its impact on user-defined code and maximally automate
parts of the framework that previously required manual instrumentation.
Further, we discover that the existing constraints of balanced environments and
``parameterized systems'' around import pose hurdles to realizing eventual
delivery and require a minor departure from the framework as defined by
Canetti~\cite{uc}.  They prohibit the necessary difference in computational
ability between the adversary and the rest of the execution that is required to
achieve eventual delivery.  Finally, we apply fuzzing and informal analysis
towards testing the liveness properties of distributed protocols.

% second research querstion
As far as we know, no work has explored using UC as an implementation framework
relying only on existing informal analysis tools which are commonplace in modern
software engineering to test and locate bugs.  Of course, such approaches can
not guarantee correct code, but we believe that programming within UC
simplifies the analysis to only assertion of the single property of
UC-indistinguishability of a protocol with an ideal functionality.  Relying on
ideal functionalities to describe protocols, and the real-ideal paradigm to
test them, is an unexplored concept, and a generalizable approach to
distributed systems programming that we believe is an improvement on the status
quo.  We address this claim, and the associated research question above, by
specifically examining whether relying on UC emulation (real-ideal
indistinguishability), suffices to catch implementation bugs in UC
implementations.  Specifically, do implementation-level bugs manifest
themselves as distinguishing environments (test cases) that fuzzing can find.
Furthermore, we confirm that UC implementations, and specifically fuzz testing,
allows implementations to analyze protocols for properties related to fairness
and probability distribution that related works don't support~\cite{some, of, the, standards}.  The
experimental method in this work consists of implementating candidate
distributed protocols, injecting bugs into them which we believe are
representative of reality, and examining the false negatives and false
positives with the lens of our research questions.  Our findings suggest that
for non-liveness bugs, even simple fuzz test generators are capable of
discovering distinguishing environments for most bugs that lead to protocol
property violation. It also provides a method for arbitrary fuzz testing of 
implementations in the standard way. 

Fuzzing isn't perfect, however, and this is expected. 
Fuzzing is only a method of finding bugs, not ruling them out.
In the case of liveness-like properties, cycle-checking is made easy as part of the UC simulator, but neither our eventual delivery model nor our attempts at being clever with import gave a significant advantage over it.
Cycle-checking for liveness failure is straightforward in deterministic protocols as evidenced by Tholoniat et al.~\cite{tholoniat2022formal}, but is complicated by non-deterministic protocols where parties can be forced into the same state multiple times due to randomness.
The false negatives we encountered for safety-like properties arose from our generators finding the adversarial action that would have forced the failure but not executing it for enough consecutive rounds. 
\todo{What did we say about these two in the main section?}

%Like any fuzz tester, it isn't always possible to catch every bug, and this is a known limitation of detecting bugs by fuzzing.
%In the case of liveness-like properties, cycle-checking is made wasy as part of the UC simulator, but neither our eventual delivery model nor our attempts at being clever with how we use import gave a significant advantage over it.
%Checking cycles also has limitations for non-deterministic protocols because a live protocol can still put parties in the same state based on randomness.
%Finally, for some safety-like properties, we encountered limitations in our test generators' ability to 

%The cases in which we fail are a consequence
%of our fuzzing strategies, and this is expected because fuzzing is only a
%method of finding bugs not ruling them out.  In the case of liveness-related
%properties, cycle-checking is made easy as part of the UC proof obligation for
%real-ideal emulation, but neither our eventual delivery model nor our attempts
%at being clever with import yield much success beyond that. 

% third question
The advantages of the ideal functionality model are evident in the cryptography
literature~\cite{people, praising, it} and were highlighted earlier in this
section.  Our attention in this paper is on understanding whether ideal
functionalities and the real-ideal paradigm provides similar advantages in
comparison to existing frameworks for protocol analysis.  The main motivator is
that no existing framework or specification language provides a truly
generalized approach to checking arbitrary properties and byzantine behaviors.
The ideal functionality approach of modelling protocol behavior as a
computation itself, doesn't require the designer to specifically encode
protocol properties as standalone statements and reduces the testing of
protocols to checking that UC emulation holds with respect to the ideal
functionality.  Most existing works do no model byzantine behavior, and those
that do are limited by assumptions on adversarial behavior and the inability to
specify, say, that the output of a coin-flipping protocol should be uniformly
distributed in the face of a computationally bounded adversary.  The adverasry
in UC is itself a small program and that can encode arbitrary behavior, so the
UC emulation relationship is a powerful security definition.  We add to the
``standard'' distributed protocols we study by examining a ``fair'' lotttery
protocol constructed from distributed coin flipping.  A distributed lottery can
be considered a canonical example blockchain protocol, and development
frameworks must be able to specify and test/check it.  It is constructed out of
distributed coin flip ideal functionality, and we check that the protocol
remains secure under composition when the functionality is replaced by
implementations of variations on coin flipping protocol.  This case study
highlights that our imlementation allows for specifying and finding bugs that
cause \emph{output fairness} failures and failures where the adversary's
knowledge allows it to influence the output of the protocol.  We do similar
experiments with the strong common coin used by the ABA protocols, checking
input and output distributions, and demonstrate that bugs causing failures in
randomness generation also manifest themselves in arbitrary protocols that only
care about safety and liveness properties.

While our 




%Our attention now turns to ideal functionalities and protocols that express
%properties relating to output fairness, adversarial influence on input/output
%(related to adversarial knowledge), and their effect on the distribution of
%outputs.  The example we use is the canonical coin flipping primitve that is
%used throughout distributed systems literature and construct a ``fair'' lottery
%out of it.  The lottery is a canonical example of the kinds of byzantine
%protocols common in the decentralized setting, but is a protocol not readily
%expressable in existing distributed development frameworks. \todo{finish} The
%canonical example we use here is the coin flips and ``fair'' lotteries which
%have become important byzantine protocols in the blockchain space, and
%implementation frameworks must be able to express thes properties in a
%protocol's specification, Some non-blockchain protocols, such as the ABA
%protocol we study in this work, make use of distributed protocols to generate
%shared common coins that must specify what the adversary learns about the
%execution and its ability to influence the outcome.  Existing frameworks fail
%to express and/or analyze protocols that require such definitions.  Not only
%does the ideal functionality enable greater expressiveness than existing
%specification frameworks in this situation, but UC's 


%Exising development and analysis frameworks fall short of desirable properties in that most lack support for byzantine protocols and for obvious reasons.
%The disparity is easily explained by the prevalence of crash-fault distributed systems in production over byzantine.
%Those that support, such as the work of Tholoniat and Gremolie~\cite{formalbyz, bymc} can not capture properties 
%and those that do, namely the work of Tholoniat and Gremolie~\cite{formalbyz, bymc} can not capture properties about adversarial influence on, or the distribution of, protocols output. 
%A simple lottery protocol, common in decentralized systens, requires fairness in availability and distribution of output, but existing framewor
%
%
%Next we implement and examine candidate byzantine protocols in this framework and analyze them for bug detection.
%There is a wealth of related frameworks that aim to support layered programming, propose a specification language for checking implementations, and some that formally verify implementations.
%The main drawback of existing works is the lack of support for byzantine protocols, and the disparity can be explained by the relative prevalence of crash-fault distributed systems compared to byzantine ones.
%%importance of crash-fault distributed systems in large scale computing compared to byzantine systems that have only recently gained widespread popularity.
%Even so, the underlying principles and techniques that these works make use of, like TLA logic to express properties, are fundamentally incompatible with the needs of the byzantine setting.
%Some works do aim at byzantine modelling for distrtibuted systems still fall short of the expressive power of UC that we aim to realize.
%For example, work by Tholoniat and Gramolie~\cite{formalbyz, bymc} uses threshold automata which can suffer from state space explosion for distributed systems with many states, can not model permissionless systems where parties may join or leave the protocol, and requires consensus algorithms be analyzed under a round-rigid adversary condition. 
%A protocol which may violate safety under an adversary that can delay parties long enough for them to fall behind can not be caught under this constraint.
%The ideal functionality model, on the other hand, expresses a desired protocols as a minimal program that expresses the properties of the protocol as a whole rather than specifying the behavior of only a single node, as in several existing works. 
%It also explicitly encodes the adversary's capabilities, and so can express desired properties about what the adversary learns about an execution of a protocol and how it can influence its outcome. 


% non-byz: fairness isn't important in non-byz and probability distributions aren't important: xor of all inputs is random and works 
% verdi: semantics for different network models, verified system transformers, extend with non-determinism for byzantine faults
% mace: single node specification because that suffices under all honest assumption
% formal byzanting verification: 

%We make the claim that a UC development framework can be used for engineering and testing distributed protocols informally, and 
%A UC-based development framework may greatly benefit programmers by offering a generalizable approach to protocol definition and testing against byzantine adversaries, and it may greatly benefit the broader UC community to create software artifacts that are easy to play with, test, and use as building blocks.
%We explore this claim by answering the following research questions:
%\begin{enumerate}
%\item Can we make better design choices to realize the UC framework and necessary network models to mimize the exposure of protocol and functionality code (user-implemented) to the underlying framework?
%\item Is the real-ideal paradigm useful for testing and analyzing protocols with informal analysis tools commonly used in software development?
%\end{enumerate}
%Security under composition is a more formal statement, and it's not clear whether there exists a straightforward validation method to substantiate it in this setting.
%
%
%The first observation we make is that US definitions tend to carry framework-specific or model-specific code alongside application-specific code.
%From a theoretical perspective, this is fine, but from a programming perspective we want minimal intereference from the framework or network model in the application itself.
%Programs and applications need to be used by other protocols, understood by programmers, and not require re-engineering for every new setting it might be used in.
%In this work, we focus on realizing and analyzing asynchronous distributed protocols, and apply these design principles to propose a new model that guarantees eventual delivery.
%Our model takes inspiration from existing works, but makes uses the import mechanism for polynomial time rather than previous, flawed, notions used in current literature.
%The proposed construction defines a wrapper around ideal functionalities, expands upon thw drawbacks of conventional UC design, and defines a new set of simple but effective design choices to automate and shift UC compleixy away from program code.
%As we discuss later in this work, the our design choices removes significant responsiblity from both protocos and environments to orchestrate the execution correctly (we defined what this means later).
%The benefits of our construction also carry over our validation strategy for the second question we answer.
%
%\todo{explain why distributed systems}
%
%In order for UC to be a useful development framework, its inherent advantages mentioned above should manifest themselves as advantages for engineering protocols.
%The obvious structural advantages give a generalized approach to writing better, more modular, code, and the ideal functionality is a more concise and expressive representation of a software package for others to interact with. 
%Despite the lack of formal guarantees on security under composition, programming within the structure provides at least some informal relationship between the ideal functuionaliy building blocks and the protocol being realized.
%The more impactful benefits are taking advantage of the real-ideal relationship as the security definition of an implementation, the environment's ability to control the adversary and adaptively choose inputs for the execution, and the 
%Finally, we care that informal analysis tools and software testing practices can be effective at analyzing protocols written with UC by relying on the indistinguishability relationship.
%
%\todo{mention that we care about bugs manifesting in the real-ideal relationship}
%We validate our claim and answer our second research question by implenting UC in a mainstream programming language, implementing asynchronous distributed protocols, and analyzing them using fuzz testing. 
%Fuzz testing is an ideal choice for UC analysis for a few reasons. 
%First, UC emulation is all about ensuring a property of the real and ideal executions holds for all environments, and relying on test case generation to create environments is a natural fit. 
%Second, fuzz testing is an effective way method of discovering bugs, even compared to formal approaches like symbolic execution, and it is widely used today in software engineering that programmers are familiar with.
%Third, the design principles that UC encourages lend themselves well to fuzz testing because protocols can be made easily separable through the ideal functionality abstraction, and the smaller state space should increase the abilities of fuzzing.  
%
%In our experiments we implement three asynchronous byzantine protocols of differing complexity. 
%The most relevant and complex protocol, an asynchronous binary agreement protocol (ABA), is an intended improvement to original version of the well-known agreement protocol by Mostefaoui et al. (dubbed the MMR protocol). 
%We implement these three protocols, and implement a fuzz testing framework for generating environments and adversarial strategies.
%In order to detect protocol implementation-level bugs through the real-ideal relationship, we inject bugs representative of those expected during development and run the faulty protocols through our fuzzing apparatus. 
%We first examine the protocols for failures unrelated to liveness or termination, and find a previously unknown vulnerability in the ABA protocol that our fuzz tester discovered.
%Furthermore, we find that for all three protocols our fuzzers only returned true positives, and failed to find a distinguishing environment in only one case (discussion in Section~\ref{sec:aba}.
%Next, we turn our attention to using our new import-based approach to polynomial time to see whether the real-ideal relationship can be useful for analyzing the liveness properties of protocols.
%Our initial approach of using the simulator proof mechanism for detecting liveness in protocols proved successful, but we observe that non-determinism in protocols makes it difficult to avoid false positives.
%Finally, we ask whether import and the environment's ability to interact with it directly aids in detecting liveness bugs.
%Our experiment shows that import ends up being minimally useful in detecting liveness bugs more successfully than the naive simulator approach, however, it is still useful for providing insight into how and when a protocol terminates with respect to the distribution of honest party inputs and adversaries. 
%
%The remainder of the paper is structured as follows.
%Section \ref{sec:background} and \ref{sec:relatedwork} describe the UC framework in more detail, along with the import mechanism, and discusses existing work in informal protocol analysis, previously proposed generalizable frameworks for distributed programming, and existing models for asynchronous networks in UC.
%Section \ref{sec:wrapper} introduces our asynchronous network model, it's unique abstraction to asyncrhonous code execution, and how it achieves eventual delivery.
%Section \ref{sec:aba} dives into our experiments with fuzzing, our setup, how our fuzzing apparatusm works, and the results of our experiments. 
%Finally, in Section \ref{sec:liveness} we examine the open problem of liveness analysis using fuzzing and our proposed eventual delivery model.

