\begin{center}
\begin{tabularx}{\textwidth}{ || p{0.2\textwidth} | p{0.1\textwidth} | p{0.1\textwidth} | p{0.5\textwidth} || }
\hline \hline
Bug(s) & Result & Generators & Remarks
\\ \hline
Message Validation ABA & TP & Simple  & Trivially found safety violation.
\\ \hline
Message Validation Ben Or & {\color{blue} FN} & - & The probabilities involved in producing the distinguishing environment and our generators need to be better and smarter about exploration.
\\ \hline
Reset \emph{bin\_ptr} [ABA] & TP / (Partial FP) & simple & liveness failure: partial FP because even inputs that result in decisions don't always output due to the structure of our implementation
\\ \hline
{\color{Maroon} Discovered: Any $(n-t)$ $\msf{AUX}(\cdot)$ [ABA]} & {\color{Maroon} Expected FP found FN} & {\color{Maroon} Targeted}  & {\color{Maroon} The protocol, as stated, exchibits a safety violation, and this was discovered as a bug in the ``correct'' protocol}
\\ \hline
Old MMR bug [ABA] & Partial FN & - & Our generators exploit it but not enough to force simulator to raise a failure.
\\ \hline 
Thresh. ABA Too Low / Too High & TP / (TP/TN) & Simple / simple & common coin eases ability to detect / Deadlocks in some cases + simulator without manual inspection highlighted the failure.
\\ \hline
Thresh. BenOr Too Low / Too High & TN / (TP/TN) & Targetted / Simple & Protocol over secure no exploit found without significant change in thresholds. / Deadlocks are easy to spot and live locks require manual inspection. 
\\ \hline
%{\begin{tabularx}{\textwidth}{ p{0.5\textwidth} p{0.5\textwidth} }
%\multirow{2}{1em}{Thresh.} & Too low \\ & Too high \\
%\end{tabularx}}
%& 
%{\begin{tabularx}{\textwidth}{ p{\textwidth} }
%TP \\ TP / TN
%\end{tabularx}} & 
%{\begin{tabularx}{\textwidth}{ p{\textwidth} }
%every environment \\ dumb generators
%\end{tabularx}} &
%{\begin{tabularx}{\textwidth}{ p{\textwidth} }
%safety violations \\
%some implut distributions, protocol is locked
%\end{tabularx}} \\ \hline
%every environment & Too low: safety violations \\
%& Too high: true positive / true negatives & dumb generators & Too high: some input distributions, protocol is locked
%\\ \hline
%\multirow{2}{4em}{ABA thresh. perturbation [ABA]} & Too low: true negative & every environment & Too low: safety violations \\
%& Too high: true positive / true negative & dumb generators & Too high: some distributions yield a locked protocol state
%\\ \hline
Inverted \m{supportCoin} [ABA] & TP & Simple & Simulator loop checking identifies this as a repeated cycle occuring too often to discount as randomness. 
\\ \hline
%Should present a liveness failure under specific conditions. It's rare to see exxecutions that exploit this, but some observations when partyh input is split equally. Looping behavior is a good indicator if searched over varying numbers of rounds to discound false positives. \\
\hline
\end{tabularx}
\end{center}
